%% ----------------------------------------------------------------
%% Appendix: Hardware details
%% ----------------------------------------------------------------
%!TeX root = subfile
\label{chapter:appendixE}
\markboth{Appendix E Hardware details}{Appendix E Hardware details}
\documentclass[../main.tex]{subfiles}
% ---------------------------------------------------------------- 
\begin{document}
The 3-D simulations employed throughout the thesis have been performed in the Iridis4 supercomputer at the University of Southampton.
The fluid solver is run in 128 parallel processes across 8 different nodes.
Each node is equipped with 16x 2.6 GHz Intel\textsuperscript\textregistered $ $ Sandybridge\texttrademark $ $ processors. With this set-up, 205 hours of computational time was spent for the dataset generation used in \cref{chapter:zanspy}.
A NVIDIA\textsuperscript\textregistered $ $ Tesla V100 GPU is used for training the ML model in the Iridis5 supercomputer.
It takes approximately 30 minutes to iterate through the training dataset (i.e. 30 min./epoch).

In the a-posteriori analysis, the fluid solver (Fortran) and the ML model (Python) need to run in sync.
At every time step, the resolved quantities data is transferred to the ML model in order to compute the closure terms.
After the prediction is completed, the closure terms are sent back to the fluid solver to compute the solution of the next time step.
This has been accomplished using network sockets, a data transfer protocol between processes living in the same network.
In particular, internet sockets have been employed allowing to transfer data across a network port.
An example of Fortran-Python sockets data transfer can be found in \cite{Font2019-f2py}.
Since the SANS simulation is purely 2-D, this has been carried in a 4.0 GHz Intel\textsuperscript\textregistered $ $ Core\texttrademark $\,\,$i7-6700K processor using serial computations.
It takes approximately 40 minutes to complete $\Delta t^*=10$ time units in this a-posteriori configuration.
% ---------------------------------------------------------------- 
\end{document}